---
title: "01 Data Inspection"
date: "2025-12-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
# Load necessary libraries for data manipulation and visualization
library(dplyr)
library(readr)
library(ggplot2)
library(tibble)
```

## 1. Data Source Overview

In this project, we use an open EV infrastructure dataset. It contains five CSV files at different levels of abstraction:

-   `charging_station.csv`: Station-level charging infrastructure data.
-   `charging_station_ml.csv`: City-level charging infrastructure data.
-   `country_summary.csv`: Compact country-level charging summary.
-   `world_summary.csv`: Detailed country-level infrastructure profile.
-   `ev_models.csv`: EV model-level information (brand, powertrain, origin, etc.).

In this notebook, we perform an initial inspection of these raw datasets to understand their structure, size, and basic data quality.

## 2. Load Raw Datasets

We use `read_csv` with UTF-8 encoding to ensure all characters are loaded correctly.

```{r load-data}
# Define the path to raw data
base_path <- "dataset/data_raw/"

# Load datasets with UTF-8 encoding
charging_station <- read_csv(
  paste0(base_path, "charging_station.csv"),
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)

charging_station_ml <- read_csv(
  paste0(base_path, "charging_station_ml.csv"),
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)

country_summary <- read_csv(
  paste0(base_path, "country_summary.csv"),
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)

ev_models <- read_csv(
  paste0(base_path, "ev_models.csv"),
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)

world_summary <- read_csv(
  paste0(base_path, "world_summary.csv"),
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)
```

## 3. Basic Dimensions (Rows x Columns)

We check the size of each dataset to get an idea of the data volume.

```{r dimensions}
data_dims <- tibble::tibble(
  dataset = c("charging_station",
              "charging_station_ml",
              "country_summary",
              "world_summary",
              "ev_models"),
  n_rows = c(
    nrow(charging_station),
    nrow(charging_station_ml),
    nrow(country_summary),
    nrow(world_summary),
    nrow(ev_models)
  ),
  n_cols = c(
    ncol(charging_station),
    ncol(charging_station_ml),
    ncol(country_summary),
    ncol(world_summary),
    ncol(ev_models)
  )
)

# Display the dimensions table
data_dims
```

## 4. Column Names & Types

We use `glimpse()` to preview the column names and data types (e.g., character, double).

#### 4.1 `charging_station.csv`
```{r inspect-charging-station}
glimpse(charging_station)
```

#### 4.2 `charging_station_ml.csv`
```{r inspect-charging-ml}
glimpse(charging_station_ml)
```

#### 4.3 `country_summary.csv`
```{r inspect-country-summary}
glimpse(country_summary)
```

#### 4.4 `world_summary.csv`
```{r inspect-world-summary}
glimpse(world_summary)
```

#### 4.5 `ev_models.csv`
```{r inspect-ev-models}
glimpse(ev_models)
```

## 5. Missing Values Overview

**Strategy:** We calculate the number of `NA` (missing values) in each column to determine our data cleaning strategy later.

#### 5.1 `charging_station.csv`
```{r}
colSums(is.na(charging_station))
```

#### 5.2 `charging_station_ml.csv`
```{r}
colSums(is.na(charging_station_ml))
```

#### 5.3 `country_summary.csv`
```{r}
colSums(is.na(country_summary))
```

#### 5.4 `world_summary.csv`
```{r}
colSums(is.na(world_summary))
```

#### 5.5 `ev_models.csv`
```{r}
colSums(is.na(ev_models))
```

## 6. Basic Value Distributions

**Strategy:** We plot histograms for a few key numerical variables to check for outliers or unreasonable values (e.g., negative counts).

#### 6.1 Station Count (World Level)
Checking `station_count` in the `world_summary` dataset.

```{r}
summary(world_summary$station_count)

# Using log scale because counts vary significantly between countries
ggplot(world_summary, aes(x = log10(station_count + 1))) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  labs(title = "Distribution of station_count in world_summary (Log Scale)") +
  theme_minimal()
```

#### 6.2 Station Count (City Level)
Checking `station_count` in the `charging_station_ml` dataset.

```{r}
summary(charging_station_ml$station_count)

ggplot(charging_station_ml, aes(x = log10(station_count + 1))) +
  geom_histogram(bins = 30, fill = "orange", color = "white") +
  labs(title = "Distribution of station_count in charging_station_ml (Log Scale)") +
  theme_minimal()
```

#### 6.3 EV Model Year
Checking `first_year` in the `ev_models` dataset to see the age distribution of models.

```{r}
summary(ev_models$first_year)

ggplot(ev_models, aes(x = first_year)) +
  geom_histogram(bins = 20, fill = "forestgreen", color = "white") +
  labs(title = "Distribution of EV Model Release Years") +
  theme_minimal()
```

## 7. Initial Observations

- **Data Loading:** All five CSV files were successfully loaded into R without errors.
- **Data Structure:**
    - `charging_station.csv` contains detailed station-level data, including coordinates.
    - `charging_station_ml.csv` aggregates data at the city level.
    - `world_summary` contains detailed technical indicators like `dc_fast_station_count`.
- **Data Quality:**
    - Missing values are primarily found in location-related fields (e.g., `city`, `state_province`) in the station-level data.
    - The country-level tables have very few missing values in key metrics.
    - Numeric distributions appear reasonable (no negative values for counts).
    
**Next Steps:**
Based on these observations, the raw data is relatively clean. In the next step (`02_data_preprocessing.Rmd`), we will handle the few missing values and standardize the column names for the dashboard.
