---
title: "02 Data Preprocessing"
output: html_document
date: "2025-12-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

# Load required libraries
library(readr)
library(dplyr)
library(stringr)
library(tidyverse)
library(ggplot2)
library(ineq)
```

## 1. Load Raw Datasets

We use UTF-8 encoding to ensure all characters (including special country names) are read correctly.

```{r load-data}
# Define the path to raw data
base_path <- "dataset/data_raw/"

# Load datasets with UTF-8 encoding
charging_station    <- read_csv(paste0(base_path, "charging_station.csv"), locale = locale(encoding = "UTF-8"))
charging_station_ml <- read_csv(paste0(base_path, "charging_station_ml.csv"), locale = locale(encoding = "UTF-8"))
country_summary     <- read_csv(paste0(base_path, "country_summary.csv"), locale = locale(encoding = "UTF-8"))
ev_models           <- read_csv(paste0(base_path, "ev_models.csv"), locale = locale(encoding = "UTF-8"))
world_summary       <- read_csv(paste0(base_path, "world_summary.csv"), locale = locale(encoding = "UTF-8"))
```

## 2. Task 1 Processing: Station Level Cleaning

This section handles geographic filtering, de-duplication, and power class normalization for individual charging sites.

```{r task1-processing}
# 1. Basic type adjustment & country code normalization
stations_step1 <- charging_station %>%
  mutate(
    ports        = as.integer(ports),
    country_code = toupper(country_code)
  )

# 2. Geographic validity filtering (removing missing/invalid coordinates)
stations_step2 <- stations_step1 %>%
  filter(
    !is.na(latitude), !is.na(longitude),
    dplyr::between(latitude, -90, 90),
    dplyr::between(longitude, -180, 180),
    !(latitude == 0 & longitude == 0)
  )

# 3. Country field cleaning (strictly 2 uppercase letters)
stations_step3 <- stations_step2 %>%
  filter(
    !is.na(country_code),
    nchar(country_code) == 2,
    str_detect(country_code, "^[A-Z]{2}$")
  )

# 4. De-duplication
stations_step4 <- stations_step3 %>%
  arrange(id) %>%
  distinct(id, .keep_all = TRUE) %>%
  distinct(latitude, longitude, .keep_all = TRUE)

# 5. Power and Port cleaning
stations_step5 <- stations_step4 %>%
  mutate(
    power_kw = ifelse(is.na(power_kw) | power_kw <= 0, NA_real_, power_kw),
    ports = ifelse(is.na(ports) | ports <= 0, NA_integer_, ports)
  )

# 6. Handle Power Class unknowns and Impute missing ports with median
median_ports <- median(stations_step5$ports, na.rm = TRUE)

stations_final <- stations_step5 %>%
  mutate(
    power_class = ifelse(power_class == "UNKNOWN" | is.na(power_class), "POWER_UNKNOWN", power_class),
    ports = ifelse(is.na(ports), median_ports, ports)
  ) %>%
  select(id, name, city, country_code, latitude, longitude, ports, power_kw, power_class, is_fast_dc)
```

## 3. Task 2 Processing: City Level Feature Engineering

This section focuses on the city-level dataset (`charging_station_ml.csv`), adding derived features like development stages.

```{r task2-processing}
# 1. Clean basic city data
ml_base <- charging_station_ml %>%
  mutate(country_code = toupper(country_code)) %>%
  filter(!is.na(latitude), !is.na(longitude), !(latitude == 0 & longitude == 0)) %>%
  mutate(
    station_count = ifelse(is.na(station_count) | station_count <= 0, NA_integer_, station_count),
    fast_station_share = ifelse(is.na(fast_station_share) | fast_station_share < 0, 0, fast_station_share),
    median_power_kw = ifelse(is.na(median_power_kw) | median_power_kw <= 0, NA_real_, median_power_kw)
  ) %>%
  filter(!is.na(station_count), !is.na(fast_station_share), !is.na(median_power_kw))

# 2. Add developmental features
ml_clean <- ml_base %>%
  mutate(
    # Create a flag for cities dominated by fast charging (>70% share, >50kW median power, min 5 stations)
    is_fast_dominant = (fast_station_share > 0.7 & median_power_kw > 50 & station_count >= 5),
    
    # Categorize cities by infrastructure maturity
    dev_stage = case_when(
      station_count < 20 & fast_station_share < 0.3 ~ "Early",
      station_count < 100 & fast_station_share < 0.5 ~ "Growth",
      station_count < 500 & fast_station_share < 0.7 ~ "Developing",
      TRUE ~ "Mature"
    ),
    
    # Log transform for better visualization scaling
    log_station_count = log10(station_count + 1)
  )
```

## 4. Task 3 Processing: World & Country Summary Cleaning

This section handles the high-level summaries, focusing on data structure integrity and outlier detection using the IQR method.

```{r task3-processing}
# 1. Basic cleaning and de-duplication
world_clean <- world_summary %>% drop_na() %>% distinct()
country_clean <- country_summary %>% drop_na() %>% distinct()

# 2. Outlier Detection Visualization
# (This plot is for report inspection only)
ggplot(world_clean, aes(x = "", y = station_count)) +
  geom_boxplot(fill = "steelblue") +
  labs(title = "Task 3: World Summary Station Count Outliers") +
  theme_minimal()

# 3. Flagging Outliers using IQR (Interquartile Range)
world_final <- world_clean %>%
  mutate(is_outlier = ifelse(station_count > (quantile(station_count, 0.75) + 1.5 * IQR(station_count)), TRUE, FALSE))

country_final <- country_clean %>%
  mutate(is_outlier = ifelse(port_count > (quantile(port_count, 0.75) + 1.5 * IQR(port_count)), TRUE, FALSE))
```

## 5. Task 4 Processing: EV Model Categorization

This section cleans the `ev_models.csv` dataset, standardizing country origins and categorizing body styles for market analysis.

```{r task4-processing}
ev_clean <- ev_models %>%
  mutate(
    # 1. Standardize Country Name (Origin)
    origin_country = str_to_lower(str_trim(origin_country)),
    origin_country = case_when(
      origin_country %in% c("us", "usa", "united states", "united state") ~ "USA",
      origin_country %in% c("uk", "united kingdom") ~ "UK",
      origin_country %in% c("de", "germany") ~ "Germany",
      origin_country %in% c("fr", "france") ~ "France",
      origin_country %in% c("se", "sweden") ~ "Sweden",
      origin_country %in% c("it", "italy") ~ "Italy",
      origin_country %in% c("jp", "japan") ~ "Japan",
      origin_country %in% c("kr", "south korea") ~ "South Korea",
      origin_country %in% c("cn", "china") ~ "China",
      TRUE ~ str_to_title(origin_country)
    ),
    
    # 2. Body Style Categorization
    style_category = case_when(
      str_detect(body_style, regex("SUV|Crossover|Pickup|Van|MPV", ignore_case = TRUE)) ~ "SUV & Utility",
      str_detect(body_style, regex("Sedan|Saloon|Liftback|Wagon|Shooting Brake", ignore_case = TRUE)) ~ "Sedan & Wagon",
      str_detect(body_style, regex("Hatchback|City|Compact", ignore_case = TRUE)) ~ "Hatchback & Compact",
      TRUE ~ "Other"
    ),
    
    powertrain = str_to_upper(powertrain)
  ) %>%
  
  # 3. Market Filtering: Retain models in Global, US, and EU markets
  filter(
    str_detect(market_regions, regex("US|EU|UK|CA|Global|America|Europe", ignore_case = TRUE))
  ) %>%
  
  # 4. Calculate Model Age (Age in 2025)
  mutate(age_2025 = 2025 - first_year)
```

## 6. Save All Cleaned Datasets

Finally, we export all cleaned datasets to the `dataset/data_clean/` directory in one batch.

```{r save-data}
# Define clean path and ensure directory exists
clean_path <- "dataset/data_clean/"
if(!dir.exists(clean_path)) dir.create(clean_path, recursive = TRUE)

# 1. Save Task 1 Data
write_csv(stations_final, paste0(clean_path, "charging_station_clean.csv"))

# 2. Save Task 2 Data
write_csv(ml_clean, paste0(clean_path, "charging_stations_ml_clean.csv"))

# 3. Save Task 3 Data
write_csv(world_final, paste0(clean_path, "cleaned_world_summary.csv"))
write_csv(country_final, paste0(clean_path, "cleaned_country_summary.csv"))

# 4. Save Task 4 Data
write_csv(ev_clean, paste0(clean_path, "ev_models_clean.csv"))

message("All cleaned datasets have been saved successfully to dataset/data_clean/")
```
