---
title: "EV Charging Analytics Dashboard"
Date: "2025-12-19"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: default
    social: []
    source_code: embed
    css: custom.css
---


```{r setup, include=FALSE}
# 1. Install & load required packages ------------------------
packages <- c(
  "flexdashboard", "knitr", "DT", "rpivotTable", "ggplot2",
  "plotly", "dplyr", "openintro", "highcharter", "ggvis",
  "leaflet", "leafgl", "sf", "readr", "ineq", "tidyverse",
  "viridis", "shiny"
)

new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages) > 0) install.packages(new_packages)

library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(leaflet)
library(leafgl)
library(sf)
library(readr)
library(ineq)
library(tidyverse)
# 2. Load all Task 1 data prep (this script defines stations_world,
#    stations_task1, stations_task1_sf, fast_mix_global, fast_country_top35, etc.)
source("R/task1_module.R")
source("R/task2_module.R")
source("R/task3_module.R")
source("R/task4_module.R")


# 3.Helper Function: Apply Dark Theme to Plotly Charts
apply_dark_theme <- function(p, title_text = NULL, show_legend = TRUE) {
  p %>% plotly::layout(
    # 1. General background and font style
    paper_bgcolor = "#0d1117",
    plot_bgcolor  = "#0d1117",
    font          = list(color = "white", family = "Calibri"),
    
    # 2. topic
    title = if (!is.null(title_text)) list(
      text = title_text,
      x    = 0.5,
      font = list(color = "white", size = 20) 
    ) else NULL,
    
    # 3. coordinator
    xaxis = list(
      tickfont  = list(color = "white"),
      titlefont = list(color = "white"),
      gridcolor = "#2c3e50" 
    ),
    yaxis = list(
      tickfont  = list(color = "white"),
      titlefont = list(color = "white"),
      gridcolor = "#2c3e50"
    ),
    
    # 4. graph
    legend = if (show_legend) list(
      font = list(color = "white", size = 12),
      bgcolor = "rgba(0,0,0,0)"
    ) else list(showlegend = FALSE),
    
    # 5. 
    margin = list(t = 60, b = 40, l = 60, r = 40)
  )
}

```


Task 1
===========================================================

Row {data-height=120}
---------------------

### Total Stations
```{r}
valueBox(
  paste0(nrow(stations_task1), "\nTotal Stations (EU & Americas)"),
  icon  = "fa-bolt"
)

```

### Total Ports
```{r}
valueBox(
  paste0(sum(stations_task1$ports, na.rm = TRUE), "\nTotal Ports"),
  icon  = "fa-plug"
)

```

### Avg Power (kW)
```{r}
valueBox(
  paste0(round(mean(stations_task1$power_kw, na.rm = TRUE), 1), "\nAvg Power (kW)"),
  icon  = "fa-tachometer"
)

```

### Countries
```{r}
valueBox(
  paste0(dplyr::n_distinct(stations_task1$country_code), "\nCountries (EU & Americas)"),
  icon  = "fa-globe"
)

```

Row {.tabset .vertical-tabs data-height=800}
---------------------

### Advanced Map

```{r}
### Advanced Map
leaflet(stations_task1_sf,options = leafletOptions(preferCanvas = TRUE)) %>%
  # Dark themed basemap
  
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  
  # WebGL point layer for all stations (colored by fast / non-fast)
  leafgl::addGlPoints(
    data        = dplyr::filter(stations_task1_sf, fast_type == "Fast-DC"),
    fillColor   = "#FFB347",
    fillOpacity = 0.5,
    radius      = 2,
    group       = "Fast-DC"
  ) %>%
  # 2. Draw normal ST second (blue on top)
  leafgl::addGlPoints(
    data        = dplyr::filter(stations_task1_sf, fast_type == "Non-fast"),
    fillColor   = "#33CCFF",
    fillOpacity = 0.5,
    radius      = 1.7,
    group       = "Non-fast"
  ) %>%
  
  # Force the initial view to focus on Europe + Americas
  # This also forces a redraw so points are visible immediately.
  fitBounds(
    lng1 = -170, lat1 = -60,   # bottom-left corner (South America / Pacific)
    lng2 =  60,  lat2 =  75    # top-right corner (Northern Europe)
  ) %>%
  
  # Legend with human-friendly labels
  addLegend(
    position = "bottomright",
    colors   = c("#33CCFF", "#FFB347"),
    labels   = c("Slow / Normal charging", "Fast DC charging"),
    title    = "Charging type",
    opacity  = 0.9
  )


```


### Charging Analysis

```{r}
# ========================
# 1. prepare p_mix (Donut)
# ========================
fast_mix_display <- fast_mix_global %>%
  dplyr::mutate(
    label_display = dplyr::recode(fast_type,
      "Fast-DC"  = "Fast DC",
      "Non-fast" = "Slow / AC"
    ),
    color_hex = ifelse(fast_type == "Fast-DC", "#FFB347", "#33CCFF"),
    pct = share * 100
  )

p_mix <- plotly::plot_ly(
  data   = fast_mix_display,
  labels = ~label_display,
  values = ~pct,
  type   = "pie",
  hole   = 0.55,
  text         = ~paste0(round(pct), "%"),
  textinfo     = "text",
  textposition = "inside",
  textfont     = list(size = 24, color = "white", family = "Calibri"), 
  hovertemplate = "%{label}<br>Share: %{value:.1f}%<extra></extra>",
  marker = list(colors = ~color_hex, line = list(color = "#0d1117", width = 1)),
  sort = FALSE
) %>%
  apply_dark_theme(title_text = "Global Charging Mix") %>%
  layout(
    legend = list(orientation = "h", x = 0.5, y = -0.1, xanchor = "center"), 
    margin = list(l = 20, r = 20, t = 60, b = 20)
  )

# ========================
# 2. prepare p_pareto (Bar)
# ========================
pareto_df <- fast_country_top35 %>%
  dplyr::mutate(
    fast_share_pct = fast_share * 100,
    cum_share_pct  = cum_fast_share * 100
  )

p_pareto <- plotly::plot_ly(pareto_df) %>%
  plotly::add_bars(
    x    = ~country_code,
    y    = ~fast_share_pct,
    name = "Share %",
    marker = list(color = "#33CCFF"),
    hovertemplate = "Country: %{x}<br>Share: %{y:.2f}%<extra></extra>"
  ) %>%
  plotly::add_lines(
    x     = ~country_code,
    y     = ~cum_share_pct,
    name  = "Cumulative %",
    yaxis = "y2",
    mode  = "lines+markers",
    line  = list(color = "warning", width = 2),
    hovertemplate = "Cumulative: %{y:.1f}%<extra></extra>"
  ) %>%
  apply_dark_theme(title_text = "Fast-DC Ports (Pareto)") %>%
  plotly::layout(
    xaxis = list(title = "", tickangle = -45),
    yaxis = list(title = "Share (%)", range = c(0, 30)),
    yaxis2 = list(
      title      = "Cumul. (%)",
      overlaying = "y",
      side       = "right",
      range      = c(0, 105),
      tickfont   = list(color = "white"),
      titlefont  = list(color = "white")
    ),
    legend = list(orientation = "h", x = 0.5, y = 1.05, xanchor = "center"),
    margin = list(l = 40, r = 40, t = 60, b = 20)
  )

# ========================
# 3. output
# ========================
shiny::fillRow(p_mix, p_pareto, flex = c(3, 7), height = "100%")

```
### Power Class Mix

```{r}


# 2. Plot Stacked Bar Chart
p_power_class <- plotly::plot_ly(
  data      = pc_df_ready,
  x         = ~country_code,
  y         = ~stations,
  color     = ~power_class,
  type      = "bar",
  hovertext = ~hover_text,
  hoverinfo = "text"
) %>%
  # 3. Apply shared dark theme
  apply_dark_theme(title_text = "Stations by Power Class (Top 35)") %>%
  
  # 4. Specific adjustments (Stack mode)
  plotly::layout(
    barmode = "stack",
    xaxis   = list(title = "", tickangle = -45),
    yaxis   = list(title = "Number of stations")
  )

p_power_class
```

Task 2
===========================================================

Row {data-height=120}
---------------------

### Total Cities
```{r}
valueBox(
  paste0(dashboard_metrics$total_sampled, "\nCities (Sampled)"),
  icon = "fa-city",
  color = "primary"
)
```

### Average Stations per City
```{r}
avg_stations <- round(mean(dashboard_data$station_count, na.rm = TRUE), 1)
valueBox(
  paste0(avg_stations, "\nAvg. Stations/City"),
  icon = "fa-charging-station",
  color = "info"
)
```

### Fast-Dominant Cities
```{r}
fast_dom <- dashboard_data %>%
  filter(fast_station_share > 0.7, median_power_kw > 50, station_count >= 5) %>%
  nrow()

valueBox(
  paste0(fast_dom, "\nFast-Dominant Cities"),
  icon = "fa-bolt",
  color = "warning"
)
```



### Gini Coefficient

```{r}
gini_val <- dashboard_metrics$gini_coefficient
valueBox(
  paste0(round(gini_val, 3), "\nGini Coefficient"),
  icon = "fa-chart-line",
  color = ifelse(gini_val > 0.6, "danger", 
                 ifelse(gini_val > 0.4, "warning", "success"))
)
```

Row {.tabset .vertical-tabs data-height=800}
---------------------



### Inequality Analysis Lorenz Curve
```{r}
#
# Lorenz Curve
create_lorenz_plot(dashboard_data, dashboard_metrics$gini_coefficient)
```
### Inequality Analysis Top 10% Cities
```{r }
# Concentration Pie Chart
create_inequality_pie(dashboard_data, top_pct = 0.1)
```






### Fast-Charging Share vs. Median Power
```{r }
# Fast-Charging Infrastructure Scatter Plot
create_fast_scatter(dashboard_data, size_by_log = TRUE)
```



### City charging Infrastructure clustering
```{r}
# 
# PCA Visualization of City Clusters
create_cluster_pca(dashboard_data, n_clusters = 9)
```




Task 3
===========================================================

Row {data-height=120}
---------------------

### Total Fast Charging Stations
```{r}
valueBox(
  paste0(sum(world_summary$fast_station_count, na.rm = TRUE), "\nTotal Fast Charging Stations"),
  icon  = "fa-bolt"
)

```

### Total Ultra Charging Stations
```{r}
valueBox(
  paste0(sum(world_summary$dc_ultra_station_count, na.rm = TRUE), "\nTotal Ultra Charging Stations"),
  icon  = "fa-rocket"
)

```

### Avg Fast Station Share
```{r}
valueBox(
  paste0(format(round(mean(world_summary$fast_station_share, na.rm = TRUE), 1), nsmall = 1), 
         "\nAvg Fast Station Share"),
  icon    = "fa-percent"
)
```


Row {.tabset .vertical-tabs data-height=800}
---------------------

### Charging Stations Bar Chart (Top 20)

```{r}
world_summary <- read_csv("dataset/data_clean/cleaned_world_summary.csv")
country_summary <- read_csv("dataset/data_clean/cleaned_country_summary.csv")

# Assuming world_summary already contains the is_european_or_us column
# Filter and sort by charging station count, keeping only countries where is_european_or_us is 1
sorted_data <- world_summary %>%
  filter(is_european_or_us == 1) %>%  # Select only European and American countries
  arrange(desc(station_count)) %>%
  mutate(rank = row_number()) %>%  # Create a ranking variable
  select(country, station_count, rank) %>%
  head(20)  # Keep only the top 20 countries

# Create the bar chart
# Modification: Add 'text' parameter inside aes() to customize the tooltip content
p <- ggplot(data = sorted_data, 
            aes(x = reorder(country, station_count), 
                y = station_count, 
                fill = station_count,
                text = paste0("Country: ", country, "\nStations: ", station_count))) + # Define custom hover text
  geom_bar(stat = "identity", width = 0.8) +
  coord_flip() +
  scale_fill_gradient(low = "#87CEEB", high = "#0a2fcc", name = "Number of Charging Stations") +
  labs(title = "Top 20 European and American Countries by Number of Charging Stations",
       x = "European and American Countries",
       y = "Number of Charging Stations") +
  scale_y_continuous(breaks = seq(0, max(sorted_data$station_count), by = 10000)) +  
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 9, family = "Arial Black", color = "white"),
        axis.text.y = element_text(size = 9, family = "Arial Black", color = "white"),
        legend.title = element_text(color = "white"),
        legend.text = element_text(color = "white"))

# Convert ggplot object to plotly object
# Modification: Set 'tooltip' to "text" to force Plotly to use only the custom text defined above
p_plotly <- ggplotly(p, tooltip = "text")

# Apply layout settings (Kept unchanged)
p_plotly <- p_plotly %>% layout(
  barmode = "stack",
  title = list(
    text = "Top 20 European and American Countries by Number of Charging Stations",
    x = 0.5,
    font = list(color = "white", size = 14)
  ),
  xaxis = list(
    title = list(font = list(color = "white")),
    tickangle = -45,
    tickfont = list(color = "white")
  ),
  yaxis = list(
    title = list(font = list(color = "white")),
    tickfont = list(color = "white")
  ),
  legend = list(
    title = list(font = list(color = "white")),
    font = list(color = "white")
  ),
  paper_bgcolor = "#0d1117",
  plot_bgcolor = "#0d1117",
  font = list(color = "white")
)

# Display the plotly graph
p_plotly
```

### Ports Bar Chart (Top 20)
```{r}
# Data processing (Keep only the top 20 countries)
sorted_data <- world_summary %>%
  filter(is_european_or_us == 1) %>%  # Select only European and American countries
  arrange(desc(port_count)) %>%
  mutate(rank = row_number()) %>%  # Create a ranking variable
  select(country, port_count, rank) %>%
  head(20)  # Keep only the top 20 countries

# Create the bar chart
# Modification: Add 'text' parameter inside aes() to customize the tooltip content
p <- ggplot(data = sorted_data, 
            aes(x = reorder(country, port_count), 
                y = port_count, 
                fill = port_count,
                text = paste0("Country: ", country, "\nPorts: ", port_count))) + # Define custom hover text
  geom_bar(stat = "identity", width = 0.8) +
  coord_flip() +
  scale_fill_gradient(low = "#fee08b", high = "#cB0000", name = "Number of Ports") +  # Gradient from yellow to red
  labs(title = "Top 20 European and American Countries by Number of Ports",
       x = "European and American Countries",
       y = "Number of Ports") +
  scale_y_continuous(breaks = seq(0, max(sorted_data$port_count), by = 10000)) +  
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 9, family = "Arial Black", color = "white"),
        axis.text.y = element_text(size = 9, family = "Arial Black", color = "white"),
        legend.title = element_text(color = "white"),  # Legend title color
        legend.text = element_text(color = "white"))

# Convert ggplot object to plotly object
# Modification: Set 'tooltip' to "text" to force Plotly to use only the custom text defined above
p_plotly <- ggplotly(p, tooltip = "text")

# Apply layout settings
p_plotly <- p_plotly %>% layout(
  barmode = "stack",
  title = list(
    x = 0.5,
    font = list(color = "white", size = 14)  # Title font color
  ),
  xaxis = list(
    title = list(font = list(color = "white")),  # Axis title color
    tickangle = -45,
    tickfont = list(color = "white")  # Tick labels color
  ),
  yaxis = list(
    title = list(font = list(color = "white")),  # Axis title color
    tickfont = list(color = "white")  # Tick labels color
  ),
  legend = list(
    title = list(font = list(color = "white")),  # Legend title color
    font = list(color = "white")  # Legend text color
  ),
  paper_bgcolor = "#0d1117",
  plot_bgcolor = "#0d1117",
  font = list(color = "white")  # Default font color for the plot
)

# Display the plotly graph
p_plotly

```
### Infrastructure Level Clustering Scatter Plot
```{r}
set.seed(123)  # Set random seed for reproducibility

# Filter to select only European and American countries
data_eu_us <- world_summary %>%
  filter(is_european_or_us == 1)

# Select indicators for clustering
clustering_data <- data_eu_us %>%
  select(station_count, max_power_kw, fast_station_share) %>%
  filter(complete.cases(.))  # Remove rows with missing values

# Standardize the indicators
clustering_scaled <- scale(clustering_data)

# Set the number of clusters
k <- 3

# Perform K-means clustering
kmeans_result <- kmeans(clustering_scaled, centers = k, nstart = 100)

# Add the cluster memberships back to the original data
data_eu_us$cluster <- as.factor(kmeans_result$cluster)

# Create a scatter plot (using station_count and fast_station_share as variables)
p <- ggplot(data_eu_us, aes(x = station_count, y = fast_station_share, 
                             color = cluster, 
                             text = paste("max_power_kw:", max_power_kw, "<br>country:", country))) +
  geom_point(size = 2) +
  labs(title = "Infrastructure Level Clustering Scatter Plot (EU & Americas)",
       x = "Number of Charging Stations",
       y = "Fast Charging Station Share",
       color = "Cluster") +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial Black", color = "white"),
    plot.title = element_text(hjust = 0.5),  # Center the plot title
    axis.title.x = element_text(color = "white"),  # Set x-axis title color
    axis.title.y = element_text(color = "white"),  # Set y-axis title color
    axis.text.x = element_text(color = "white"),  # Set x-axis text color
    axis.text.y = element_text(color = "white")   # Set y-axis text color
  )

# Convert to an interactive Plotly graph
p_plotly <- ggplotly(p)

# Set background and font colors
p_plotly <- p_plotly %>% layout(
  paper_bgcolor = "#0d1117",
  plot_bgcolor = "#0d1117",
  font = list(color = "white"),
  title = list(text = "Infrastructure Level Clustering Scatter Plot (EU & Americas)", 
               font = list(color = "white", size = 14))
)

# Display the plot
p_plotly
```


### Charging Stations Heatmap by Power Class 

```{r}
# Filter to select only European and American countries
data_eu_us <- world_summary %>%
  filter(is_european_or_us == 1)

# Ensure dc_fast_station_count and dc_ultra_station_count are numeric types
data_eu_us$dc_fast_station_count <- as.numeric(as.character(data_eu_us$dc_fast_station_count))
data_eu_us$dc_ultra_station_count <- as.numeric(as.character(data_eu_us$dc_ultra_station_count))

# Remove countries where both dc_fast_station_count and dc_ultra_station_count are less than 100
data_eu_us <- data_eu_us %>%
  filter(!(dc_fast_station_count < 100 & dc_ultra_station_count < 100))

# Create a long format dataset for heatmap
heatmap_data <- data_eu_us %>%
  select(country, dc_fast_station_count, dc_ultra_station_count) %>%
  pivot_longer(cols = c(dc_fast_station_count, dc_ultra_station_count),
               names_to = "station_type", values_to = "count")

# Use Plotly to create a heatmap
plot_ly(data = heatmap_data, 
        x = ~station_type, 
        y = ~reorder(country, count), 
        z = ~log(count + 1),  # Log transformation for better visualization
        type = "heatmap",
        colorscale = "Reds") %>%
  layout(
    title = list(
      text = "Stations by Power Class (EU & Americas)",
      x = 0.5,
      font = list(color = "white", size = 14)
    ),
    xaxis = list(
      title = "Charging Station Type",
      tickangle = 0,  # Angle for the x-axis labels
      titlefont = list(color = "white")  # Titles for axes
    ),
    yaxis = list(
      title = "Country",
      titlefont = list(color = "white")  # Titles for axes
    ),
    paper_bgcolor = "#0d1117",  # Background color of the paper
    plot_bgcolor = "#0d1117",   # Background color of the plot
    font = list(color = "white"), # General font color
    coloraxis = list(colorbar = list(title = list(text = "Count (log scale)")))  # Color bar
  )
```
Task 4
===========================================================
Row {data-height=120}
---------------------

### Total Models
```{r}
if(exists("ev_models")) {
  valueBox(
    paste0(nrow(ev_models), "\nTotal EV Models"),
    icon = "fa-car",
  )
}
```




### Dominant Style
```{r}
if(exists("ev_models")) {
  top_style <- names(sort(table(ev_models$style_category), decreasing=TRUE))[1]
  valueBox(
    paste0(top_style, "\nTop Body Style"),
    icon = "fa-trophy",
  )
}
```




### Avg Model Age
```{r}
if(exists("ev_models")) {
  avg_age <- round(mean(ev_models$age_2025, na.rm=TRUE), 1)
  valueBox(
    paste0(avg_age, " Years\nAvg Model Age"),
    icon = "fa-clock-o",
  )
}
```




### Active Markets
```{r}
if(exists("ev_models")) {
  n_countries <- n_distinct(ev_models$origin_country)
  valueBox(
    paste0(n_countries, "\nOrigin Countries"),
    icon = "fa-globe",
  )
}
```




Row {.tabset .vertical-tabs data-height=800}
---------------------

### Global Market Structure

```{r}
if(exists("ev_models")) {
  pie_data <- ev_models %>% count(style_category) %>% mutate(pct = n/sum(n)*100)
  
  plot_ly(pie_data, labels = ~style_category, values = ~n, type = 'pie',
          hole = 0.55,
          textinfo = 'label+percent',
          textfont = list(color = "white"),
          marker = list(colors = c('#33CCFF', '#FFB347', '#00cc96', '#ab63fa'),
                        line = list(color = "#0d1117", width = 1))) %>% 
    layout(
      title = list(text = "Global EV Market by Body Style", font = list(color = "white", size = 14)),
      paper_bgcolor = task4_theme$paper_bgcolor,
      plot_bgcolor  = task4_theme$plot_bgcolor,
      font = task4_theme$font,
      showlegend = TRUE,
      legend = task4_theme$legend,
      margin = list(t = 50, b = 20, l = 20, r = 20)
    )
}
```

### Regional Preferences

```{r}
if(exists("ev_models")) {
  heatmap_data <- ev_models %>%
    count(origin_country, style_category) %>%
    pivot_wider(names_from = style_category, values_from = n, values_fill = 0)
  
  plot_ly(
    x = colnames(heatmap_data)[-1],
    y = heatmap_data$origin_country,
    z = as.matrix(heatmap_data[, -1]),
    type = "heatmap",
    colors = "Blues",
    hovertemplate = paste("Country: %{y}<br>Style: %{x}<br>Count: %{z}<extra></extra>")
  ) %>%
    layout(
      title = list(text = "Regional Preference (Heatmap)", font = list(color = "white", size = 14)),
      xaxis = modifyList(task4_theme$xaxis, list(title = "Body Style")),
      yaxis = modifyList(task4_theme$yaxis, list(title = "Origin Country")),
      paper_bgcolor = task4_theme$paper_bgcolor,
      plot_bgcolor  = task4_theme$plot_bgcolor,
      font = task4_theme$font,
      margin = list(t = 50, b = 50, l = 50, r = 20)
    )
}
```

### Infrastructure Level Clustering Scatter Plot

```{r}
if(exists("ev_models")) {
  plot_ly(ev_models, x = ~origin_country, y = ~age_2025, color = ~origin_country, type = "box") %>%
    layout(
      title = list(text = "Innovation Speed: Model Age Distribution", font = list(color = "white", size = 14)),
      xaxis = modifyList(task4_theme$xaxis, list(title = "Country")),
      yaxis = modifyList(task4_theme$yaxis, list(title = "Model Age (Years)")),
      paper_bgcolor = task4_theme$paper_bgcolor,
      plot_bgcolor  = task4_theme$plot_bgcolor,
      font = task4_theme$font,
      showlegend = FALSE,
      margin = list(t = 50, b = 40, l = 40, r = 20)
    )
}
```



Data Tables
===========================

Row {.tabset}
---------------------

### Global Stations

```{r}
# Use DT for interactive searching/sorting without a server
if(exists("stations_world")) {
  DT::datatable(
    stations_world,
    options = list(
      pageLength = 20,    # Show 15 rows per page
      scrollX = TRUE,     # Allow horizontal scrolling
      dom = 'Bfrtip'      # Basic layout elements
    )
  )
}
```

### City Stations
```{r}
if(exists("stations_city")) {
  DT::datatable(
    stations_city,
    options = list(pageLength = 20, scrollX = TRUE)
  )
}
```

### World Summary
```{r}
if(exists("world_summary")) {
  DT::datatable(
    world_summary,
    options = list(pageLength = 20, scrollX = TRUE)
  )
}
```

### Country Summary
```{r}
if(exists("country_summary")) {
  DT::datatable(
    country_summary,
    options = list(pageLength = 20, scrollX = TRUE)
  )
}
```

### EV Models
```{r}
if(exists("ev_models")) {
  DT::datatable(
    ev_models,
    options = list(pageLength = 20, scrollX = TRUE)
  )
}
```

